Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-04 paper_jasa.tex
supplimentary plot updated

\begin{figure}[hbtp]
   \centering
       \scalebox{0.55}{\includegraphics{power_loess_effect.pdf}}
       \caption{Power in comparison to effect for the three experiments. Points indicate subject responses, with size indicating count. Responses are 1 and 0 depending on the success or failure respectively to identify the actual plot in the lineup. The loess curve (blue) estimates the observed power, and grey bands show simultaneous bootstrap confidence band.  Conventional test power is drawn as a dashed line. For experiment 3, conventional power is based on the slopes of the linear part of the non-contaminated data. Power for contaminated data is shown by cross mark.
}
       \label{fig:power_loess_effect}
\end{figure}

@@

In the previous section we noticed that observers tend to pick the plot with the lowest $p$-value. If a null plot has data that, by chance because the sample is a random draw from the null, has a smaller $p$-value than the actual data, we would expect that there is a strong possibility that an observer will pick this null plot instead of the actual data plot. Figure \ref{fig:pval_difference} investigates this for the data collected in experiments 1 and 2. The plots display the proportion of observers who choose the actual data plot against the $p$-value of the actual data minus the lowest seen in the null data. A small negative value of the difference means that the $p$-value of the actual data is smaller than that of the null data. If there is a big negative difference we'd expect to see We would expect to see that the observers would more often make the correct choice of plot. This can be seen. When there is a large positive difference If however, there is little difference between the $p$-values then we'd expect to see more confusion in the choices.

\green{Something is definitely not right! The code looks like it does actual data p-value - min(null $p$-value). But how can you get a difference of 0.8 from this??} \blue{It is possible theoretically! Suppose data plot $p$-value is larger than 0.8. Under null hypothesis, $p$-value $\sim U(0,1)$. Thus min(null $p$-value) could close to zero by chance producing this large difference. And this has happened in both experiment 1 and 2.}

>>>>

\begin{figure}[hbtp]
   \centering
       \scalebox{0.55}{\includegraphics{power_loess_effect.pdf}}
       \caption{Power in comparison to effect for the three experiments. Points indicate subject responses, with size indicating count. Responses are 1 and 0 depending on the success or failure respectively to identify the actual plot in the lineup. The loess curve (blue) estimates the observed power, and grey bands show simultaneous bootstrap confidence band.  Conventional test power is drawn as a dashed line. For experiment 3, conventional power is based on the slopes of the linear part of the non-contaminated data. Power for contaminated data is shown by cross mark.}
       \label{fig:power_loess_effect}
\end{figure}

@@

In the previous section we noticed that observers tend to pick the plot with the lowest $p$-value. If a null plot has data that, by chance because the sample is a random draw from the null, has a smaller $p$-value than the actual data, we would expect that there is a strong possibility that an observer will pick this null plot instead of the actual data plot. Figure \ref{fig:pval_difference} investigates this for the data collected in experiments 1 and 2. The plots display the proportion of observers who choose the actual data plot against the $p$-value of the actual data minus the lowest seen in the null data. A small negative value of the difference means that the $p$-value of the actual data is smaller than that of the null data. If there is a big negative difference we'd expect to see that the observers would more often make the correct choice of plot. When there is a large positive difference, observers fail to pick the correct plot. If however, there is little difference between the $p$-values then we'd expect to see more confusion in the choices.

\green{Something is definitely not right! The code looks like it does actual data p-value - min(null $p$-value). But how can you get a difference of 0.8 from this??} \blue{It is possible theoretically! Suppose data plot $p$-value is larger than 0.8. Under null hypothesis, $p$-value $\sim U(0,1)$. Thus min(null $p$-value) could be close to zero by chance producing this large difference. And this has happened in both experiment 1 and 2.}
